Semantic Prediction in {R}ussian

### 2020-04-11 paper.tex
more random reworkings

We classified these contexts based on their constraining ability and found out the following groups of com:
\newline

Semantically constraining contexts [contexts \#3, 4, 6, 8]

Syntactically constraining contexts [context \#1]

Idiomatically constraining contexts [contexts \#2, 5, 7, 9, 10]
\newline

@@

Another important aspect of the study of the linguistic model of the cloze task is the relationship between the length of the context and the probability of predicting (=predictability of) the correct word.

@@

In this case, there is practically no correlation: Pearson correlation score is 0.093521, Spearman correlation - 0.079094.

@@

It is noticeable that BERT mean accuracy results are higher than the cloze task score. This can be explained by the fact that the model was trained on a large number of written texts and thus had a higher chance to guess the correct word. Following this assumption, an assumption can be made that respondents’ active vocabulary size is lower than the model’s vocabulary. Also, we can make a hypothesis that the process of word retrieval by humans and by the model is performed differently, as respondents do not always respond with the most probable answer.

@@

Next, we compared models’ performances using an inclusion-exclusion principle to find a percentage of overlapping answers between different models. The result of this comparison is shown on the heat map below.

>>>>

We classified these contexts based on their constraining ability:
\begin{itemize}
	\item Semantically constraining contexts (contexts \#3, 4, 6, 8)
	\item Syntactically constraining contexts (context \#1)
	\item Idiomatically constraining contexts (contexts \#2, 5, 7, 9, 10)
\end{itemize}

@@

Another important aspect of the study of the linguistic model of the cloze task is the relationship between the length of the context and the probability of predicting (i.e., predictability of) the correct word.

@@

In this case, there is practically no correlation: Pearson correlation score is \(0.09\), and Spearman correlation is \(0.08\).

@@

It is noticeable that BERT mean accuracy results are higher than the cloze task score. This can be explained by the fact that the model was trained on a large number of written texts and thus had a higher chance to guess the correct word. Following this assumption, it is possible to infer respondents' active vocabulary size is lower than the model's vocabulary. Also, we can make a hypothesis that the process of word retrieval by humans and by the model is performed differently, as respondents do not always respond with the most probable answer.

@@

Next, we compared models’ performances using an inclusion-exclusion principle to find the percentage of overlapping answers between different models. The result of this comparison is shown on the heat map below.
